Binary Latent Representations for Efficient Ranking

### 2017-08-14 paper/paper.tex
Update table notes.

\section{Experiments}
\begin{table*}[htbp]
\begin{threeparttable}
\caption{Movielens 1M results}
\label{tb:results}
\centering
\begin{tabular}{rrrrrrrr}
\toprule
Dimension &   MRR & Binary MRR & MRR ratio\tnote{1} &   PPMS\tnote{2} & Binary PPMS & PPMS ratio & Memory use ratio \\
\midrule
       32 & 0.077 &      0.059 &     0.768 & 87,758 &     264,146 &      3.010 &            0.091 \\
       64 & 0.075 &      0.066 &     0.878 & 45,992 &     220,833 &      4.802 &            0.062 \\
      128 & 0.076 &      0.071 &     0.935 & 23,870 &     166,252 &      6.965 &            0.047 \\
      256 & 0.078 &      0.071 &     0.908 & 12,284 &     190,131 &     15.477 &            0.039 \\
      512 & 0.080 &      0.073 &     0.912 &   6074 &     122,637 &     20.190 &            0.035 \\
     1024 & 0.080 &      0.075 &     0.936 &   3056 &      61,301 &     20.056 &            0.033 \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\small{
\item[1] Ratio of binary model MRR to real-valued model MRR
\item[2] Predictions Per Millisecond
}
\end{tablenotes}
\end{threeparttable}
\end{table*}
To assess the accuracy-speed trade-offs enabled by the XNOR approach, we conduct an experiment on the Movielens 1M dataset \citep{harper2016movielens}. The dataset contains 1 million ratings from 6000 users on 4000 movies. Because the computational speed improvements offered by the binary representations are linear in the size of the catalogue, the results on this dataset should be indicative of results that can be obtained on larger datasets. At the same time, the dataset's small size enables us to easily test hyperparameter configurations and estimate models with high latent dimensions.

>>>>

\section{Experiments}
\begin{table*}[htbp]
\begin{threeparttable}
\caption{Movielens 1M results}
\label{tb:results}
\centering
\begin{tabular}{rrrrrrrr}
\toprule
Dimension &   MRR & Binary MRR & MRR ratio\tnote{1} &   PPMS\tnote{2} & Binary PPMS & PPMS ratio\tnote{3} & Memory use ratio\tnote{4} \\
\midrule
       32 & 0.077 &      0.059 &     0.768 & 87,758 &     264,146 &      3.010 &            0.091 \\
       64 & 0.075 &      0.066 &     0.878 & 45,992 &     220,833 &      4.802 &            0.062 \\
      128 & 0.076 &      0.071 &     0.935 & 23,870 &     166,252 &      6.965 &            0.047 \\
      256 & 0.078 &      0.071 &     0.908 & 12,284 &     190,131 &     15.477 &            0.039 \\
      512 & 0.080 &      0.073 &     0.912 &   6074 &     122,637 &     20.190 &            0.035 \\
     1024 & 0.080 &      0.075 &     0.936 &   3056 &      61,301 &     20.056 &            0.033 \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\small{
\item[1] Ratio of binary model MRR to real-valued model MRR
\item[2] Predictions Per Millisecond: how many items can be scored per millisecond
\item[3] Ratio of binary PPMS to real-valued PPMS
\item[4] Ratio of memory required to store binary vs. real-valued parameters
}
\end{tablenotes}
\end{threeparttable}
\end{table*}
To assess the accuracy-speed trade-offs enabled by the XNOR approach, we conduct an experiment on the Movielens 1M dataset \citep{harper2016movielens}. The dataset contains 1 million ratings from 6000 users on 4000 movies. Because the computational speed improvements offered by the binary representations are linear in the size of the catalogue, the results on this dataset should be indicative of results that can be obtained on larger datasets. At the same time, the dataset's small size enables us to easily test hyperparameter configurations and estimate models with high latent dimensions.
